### 2022-06-02 main/chapter_2ljets.tex
standardize 0.5em; improve vrss caption

\begin{table}[tp]
\centering
\begin{tabular}{c}
Preselection:
\\[1em]
$n_\mathrm{leptons}^\mathrm{signal} = n_\mathrm{leptons}^\mathrm{baseline} = 2$
\\[.5em]
same flavour, opposite charge leptons
\\[.5em]
$\njet \geq 1$
\\[.5em]
$p_\mathrm{T}^{\,\ell_2} > 25$
\\[.5em]
$\met > 100$
\\[.5em]
$\metsig > 6$
\end{tabular}
\caption{%
`Preselection' requirements ensured prior to all region definitions in the
$\twoljets$-electroweak search.
}
\label{tab:2ljets_presel}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_*$
& $\rjj$
\\[1em]
SR-High
& $\geq2$
& $\leq 1$
& $18\textrm{--}21\textrm{--}\infty$
& $\mjj\!:~  60\textrm{--}110$
& $0\textrm{--}0.8\textrm{--}1.6$
\\[.5em]
\: VR-High
& $\geq2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 1.6$
\\[.5em]
\: VR-High-R
& $\geq 2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  > 20}$
& $\uwave{> 1.6}$
\\[1em]
SR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\mjetone\!:~  60\textrm{--}110$
&
\\[.5em]
\: VR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\uwave{\mjetone\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
&
\\[1em]
SR-$\llbb$
& $\geq 2$
& $\geq 2$
& $> 18$
& $\mbb\!:~  60\textrm{--}150$
&
\\[.5em]
\: VR-$\llbb$
& $\geq 2$
& $\geq 2$
& $\uwave{12\textrm{--}18}$
& $\mbb\!:~  60\textrm{--}150$
&
\end{tabular}
\\[1em]
Common: Preselection,
$\mll \in 71\textrm{--}111$, and
$\mttwoll > 80$.
\caption[
High region definitions in the $\twoljets$-electroweak analysis
]{%
High region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_high}
\end{table}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRHigh8.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRHigh16.png}
\caption{}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRHigh.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRHighR.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_high_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRHigh4.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjetone_SRHigh4.png}
\caption{}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRHigh4.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjetone_VRHigh4.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_high_1j_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRllbb.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mbb_SRllbb.png}
\caption{}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRllbb.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mbb_VRllbb.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_high_llbb_region}
\end{figure}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $\mjj$
& $\ptjone$
\\[1em]
SR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}15\textrm{--}18$
& $60\textrm{--}110$
& $> 60$
\\[.5em]
\: VR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $60\textrm{--}110$
& $\uwave{< 60}$
\\[1em]
CR-VZ
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $\uwave{\hphantom{< 60}}$
\\[.5em]
CR-tt
& $\geq 2$
& $\uwave{\geq 1}$
& $\uwave{9\textrm{--}12}$
& $\uwave{20}$
& $> 60$
\end{tabular}
\\[1em]
Common: Preselection,
$\njet \geq 2$,
$\mll \in 81\textrm{--}101$, and
$\mttwoll > 80$.
\caption[
Intermediate region definitions in the $\twoljets$-electroweak analysis
]{%
Intermediate region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_int}
\end{table}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRInt.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRInt.png}
\caption{}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRInt.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRInt.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_int_region}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRZZ.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRZZ.png}
\caption{}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRtt.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRtt.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_int_cr_region}
\end{figure}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lcccccccc}
& $\metsig$
& $\mjj$
& $\mttwoll$
& $\rll$
& $\dphillmet$
\\[1em]
SR-Low
& $6\textrm{--}9\textrm{--}12$
& $60\textrm{--}110$
& $> 80$
& $< 1$
&
\\[.5em]
\: VR-Low
& $6\textrm{--}12$
& $60\textrm{--}110$
& $>80$
& $\uwave{1\textrm{--}1.4}$
&
\\[1em]
SR-Low-2
& $6\textrm{--}9$
& $60\textrm{--}110$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[.5em]
\: VR-Low-2
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[1em]
CR-Z
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $> 80$
& $\uwave{\hphantom{< 1.6}}$
& $\uwave{\hphantom{< 0.6}}$
\end{tabular}
\\[1em]
Common: Preselection,
$\njet = 2$,
$\nbtag = 0$, and
$\mll \in 81\textrm{--}101$.
\caption[
Low region definitions in the $\twoljets$-electroweak analysis
]{%
Low region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_low}
\end{table}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRLow.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRLow.png}
\caption{}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRLow.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRLow.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_low_region}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRLow2.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRLow2.png}
\caption{}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRLow2.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRLow2.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_low2_region}
\end{figure}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\metsig$
& $\mll$
& $\mttwoll$
& $\ptjone$
& $\dphijmet$
\\[1em]
SR-OffShell
& $>9$
& $12\textrm{--}40\textrm{--}71$
& $>100$
& $>100$
& $>2$
\\[.5em]
\: VR-OffShell
& $>9$
&  12--71
& $\uwave{80\textrm{--}100}$
& $> 100$
& $> 2$
\\[1em]
CR-DY
& $\uwave{6\textrm{--}9}$
& $12\textrm{--}71$
& $> 100$
& $\uwave{\hphantom{> 100}}$
& $\uwave{\hphantom{> 2}}$
\end{tabular}
\\[1em]
Common: Preselection,
$\njet \geq 2$, and
$\nbtag = 0$.
\caption[
Off-shell region definitions in the $\twoljets$-electroweak analysis
]{%
Off-shell region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_offshell}
\end{table}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SROffShell.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mll_SROffShell.png}
\caption{}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VROffShell.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mll_VROffShell.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_offshell_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRHigh.png}
\caption{DR-High}
\end{subfigure}
\quad\quad
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRllbb.png}
\caption{DR-$\llbb$}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRInt.png}
\caption{DR-Int}
\end{subfigure}
\quad\quad
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRLow.png}
\caption{DR-Low}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DROffShell.png}
\caption{DR-OffShell}
\end{subfigure}
\caption[
Pre-fit yields in discovery regions
]{%
Pre-fit yields in discovery regions.
Errors are statistical.
}
\label{fig:2ljets_disco_prefit}
\end{figure}

@@

>>>>

\begin{table}[tp]
\centering
\begin{tabular}{c}
Preselection:
\\[1em]
$n_\mathrm{leptons}^\mathrm{signal} = n_\mathrm{leptons}^\mathrm{baseline} = 2$
\\[0.5em]
same flavour, opposite charge leptons
\\[0.5em]
$\njet \geq 1$
\\[0.5em]
$p_\mathrm{T}^{\,\ell_2} > 25$
\\[0.5em]
$\met > 100$
\\[0.5em]
$\metsig > 6$
\end{tabular}
\caption{%
`Preselection' requirements ensured prior to all region definitions in the
$\twoljets$-electroweak search.
}
\label{tab:2ljets_presel}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_*$
& $\rjj$
\\[1em]
SR-High
& $\geq2$
& $\leq 1$
& $18\textrm{--}21\textrm{--}\infty$
& $\mjj\!:~  60\textrm{--}110$
& $0\textrm{--}0.8\textrm{--}1.6$
\\[0.5em]
\: VR-High
& $\geq2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 1.6$
\\[0.5em]
\: VR-High-R
& $\geq 2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  > 20}$
& $\uwave{> 1.6}$
\\[1em]
SR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\mjetone\!:~  60\textrm{--}110$
&
\\[0.5em]
\: VR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\uwave{\mjetone\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
&
\\[1em]
SR-$\llbb$
& $\geq 2$
& $\geq 2$
& $> 18$
& $\mbb\!:~  60\textrm{--}150$
&
\\[0.5em]
\: VR-$\llbb$
& $\geq 2$
& $\geq 2$
& $\uwave{12\textrm{--}18}$
& $\mbb\!:~  60\textrm{--}150$
&
\end{tabular}
\\[1em]
Common: Preselection,
$\mll \in 71\textrm{--}111$, and
$\mttwoll > 80$.
\caption[
High region definitions in the $\twoljets$-electroweak analysis
]{%
High region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_high}
\end{table}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRHigh8.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRHigh16.png}
\caption{}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRHigh.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRHighR.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_high_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRHigh4.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjetone_SRHigh4.png}
\caption{}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRHigh4.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjetone_VRHigh4.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_high_1j_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRllbb.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mbb_SRllbb.png}
\caption{}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRllbb.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mbb_VRllbb.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_high_llbb_region}
\end{figure}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $\mjj$
& $\ptjone$
\\[1em]
SR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}15\textrm{--}18$
& $60\textrm{--}110$
& $> 60$
\\[0.5em]
\: VR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $60\textrm{--}110$
& $\uwave{< 60}$
\\[1em]
CR-VZ
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $\uwave{\hphantom{< 60}}$
\\[0.5em]
CR-tt
& $\geq 2$
& $\uwave{\geq 1}$
& $\uwave{9\textrm{--}12}$
& $\uwave{20}$
& $> 60$
\end{tabular}
\\[1em]
Common: Preselection,
$\njet \geq 2$,
$\mll \in 81\textrm{--}101$, and
$\mttwoll > 80$.
\caption[
Intermediate region definitions in the $\twoljets$-electroweak analysis
]{%
Intermediate region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_int}
\end{table}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRInt.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRInt.png}
\caption{}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRInt.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRInt.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_int_region}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRZZ.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRZZ.png}
\caption{}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRtt.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRtt.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_int_cr_region}
\end{figure}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lcccccccc}
& $\metsig$
& $\mjj$
& $\mttwoll$
& $\rll$
& $\dphillmet$
\\[1em]
SR-Low
& $6\textrm{--}9\textrm{--}12$
& $60\textrm{--}110$
& $> 80$
& $< 1$
&
\\[0.5em]
\: VR-Low
& $6\textrm{--}12$
& $60\textrm{--}110$
& $>80$
& $\uwave{1\textrm{--}1.4}$
&
\\[1em]
SR-Low-2
& $6\textrm{--}9$
& $60\textrm{--}110$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[0.5em]
\: VR-Low-2
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 80$
& $< 1.6$
& $< 0.6$
\\[1em]
CR-Z
& $6\textrm{--}9$
& $\uwave{20\textrm{--}60 \mid 60\textrm{--}110}$
& $> 80$
& $\uwave{\hphantom{< 1.6}}$
& $\uwave{\hphantom{< 0.6}}$
\end{tabular}
\\[1em]
Common: Preselection,
$\njet = 2$,
$\nbtag = 0$, and
$\mll \in 81\textrm{--}101$.
\caption[
Low region definitions in the $\twoljets$-electroweak analysis
]{%
Low region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_low}
\end{table}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRLow.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRLow.png}
\caption{}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRLow.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRLow.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_low_region}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRLow2.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRLow2.png}
\caption{}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRLow2.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRLow2.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_low2_region}
\end{figure}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\metsig$
& $\mll$
& $\mttwoll$
& $\ptjone$
& $\dphijmet$
\\[1em]
SR-OffShell
& $>9$
& $12\textrm{--}40\textrm{--}71$
& $>100$
& $>100$
& $>2$
\\[0.5em]
\: VR-OffShell
& $>9$
&  12--71
& $\uwave{80\textrm{--}100}$
& $> 100$
& $> 2$
\\[1em]
CR-DY
& $\uwave{6\textrm{--}9}$
& $12\textrm{--}71$
& $> 100$
& $\uwave{\hphantom{> 100}}$
& $\uwave{\hphantom{> 2}}$
\end{tabular}
\\[1em]
Common: Preselection,
$\njet \geq 2$, and
$\nbtag = 0$.
\caption[
Off-shell region definitions in the $\twoljets$-electroweak analysis
]{%
Off-shell region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_offshell}
\end{table}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SROffShell.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mll_SROffShell.png}
\caption{}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VROffShell.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mll_VROffShell.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_offshell_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRHigh.png}
\caption{DR-High}
\end{subfigure}
\quad\quad
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRllbb.png}
\caption{DR-$\llbb$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRInt.png}
\caption{DR-Int}
\end{subfigure}
\quad\quad
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRLow.png}
\caption{DR-Low}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DROffShell.png}
\caption{DR-OffShell}
\end{subfigure}
\caption[
Pre-fit yields in discovery regions
]{%
Pre-fit yields in discovery regions.
Errors are statistical.
}
\label{fig:2ljets_disco_prefit}
\end{figure}

@@

Figure~\ref{fig:2ljets_vrss}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrss_VR_SS_EWK_met_Sign.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrss_VR_SS_EWKMC_met_Sign.png}
\caption{}
\end{subfigure}
\caption[
Same-sign validation with Matrix Method and Monte Carlo fake estimates
]{%
Same-sign validation with (a) Matrix Method and (b) Monte Carlo fake estimates.
Backgrounds are pre-fit.
Errors are statistical summed in quadrature with variations in Matrix Method
sample weights.
Those weight variations are coupled between bins, meaning that the
directed differences between bins are less significant than an independent
combination.
The Monte Carlo estimate is clearly more accurate.
\\[0.5em]
% thesis_project/2ljets/vrss_plots/PAM_FNP_50pc.pdf
Part (a) was included in an early draft of the paper.
It was removed after validation studies showed that adding an additional
$50\%$ uncertainty to fake/non-prompt yields, coupled between all bins, did not
significantly change our exclusion contours;
most contours shrank by less than their plotted line width.
The largest change was a $2\%$ reduction in the
$B(\neutralino_1 \rightarrow h \gravitino)$
limit at $m(\neutralino_1) \approx 500\,\eV[G]$.
}
\label{fig:2ljets_vrss}
\end{figure}
